---
title: "Estimating growth rates from age-at-size data"
vignette: >
  %\VignetteIndexEntry{Estimating growth rates from age-at-size data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

I still need to write this vignette.

```{r}
library(growthEstimation)
pars <- list(
    k = 0.1,
    L_inf = 110,
    d = 1,
    m = 1,
    annuli_date = 0,
    annuli_min_age = 0,
    spawning_mu = 0.4,
    spawning_kappa = 10
)

age_at_length <- Cod_CS_age_at_length

plotAgeLikelihood(pars, age_at_length)
```

To start tuning parameters, run the following code. A Shiny app will open
```{r, eval=FALSE}
tune_pars(pars, age_at_length)
```

You can automatically tune the parameters with
```{r}
fit <- fit_tmb_nll(pars, surveys = age_at_length)

pars <- fit$pars
plotAgeLikelihood(pars, age_at_length)
```

The parameters appear to fit the age-at-size data, but the mortality and diffusion
coefficients are too low. The estimated parameters are:
```{r}
parameter_names <- c("k", "L_inf", "d", "m")
pars[parameter_names]
```


This leads to the following time evolution of a yearly
cohort:
```{r}
u <- getNumberDensity(pars, l_max = 200, t_max = 15)
plotDensity2D(u)
```

```{r}
plotDensity3D(u)
```

If we constrain the mortality coefficient to be at least 30 we get:
```{r}
fit <- fit_tmb_nll(pars, surveys = age_at_length,
                   lower = c(m = 25))

pars <- fit$pars
plotAgeLikelihood(pars, age_at_length)
```

```{r}
pars[parameter_names]
```

This leads to a more realistic time evolution of a yearly cohort:
```{r}
u <- getNumberDensity(pars, l_max = 200, t_max = 15)
plotDensity2D(u)
```
```{r}
plotDensity3D(u, l_min = 20)
```

The solution including all yearly cohorts looks as follows:
```{r}
u_periodic <- getPeriodicNumberDensity(pars, l_max = 200, t_max = 3)
plotDensity3D(u_periodic, l_min = 20)
```

